Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments

### 2024-02-11 article/alt_article.qmd
Update alt_article.qmd
ss
s

    fontsize: 11pt
    cite-method: natbib

---

@@

[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-ifs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).

>>>>

    fontsize: 11pt
    csl: "templates/apa-no-ampersand.csl"
    template-partials: 
      - "templates/title.tex"
      - "templates/before-body.tex"
      - "templates/_authors.tex"      
---

@@

[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see @eq-ifs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).
